Carbonate chemistry at Ny-Ålesund

### 2022-03-30 awipev-CO2.Rmd
misc

p_f_air_sea <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
p_f_air_sea
ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")

>>>>

p_f_air_sea <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
p_f_air_sea
ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
